**The Role of Interoception and Theory of Mind in Deception**

### 2021-12-18 1_Measures.Rmd
added interpretations

- Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100`
- Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100`
- Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100`

>>>>

Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %

### 2021-12-18 3_ToM.Rmd
added interpretations

- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in interrogation than polygraph condition.

@@

@@

@@

@@

@@

>>>>

- Confidence: effect in total, cognitive and physical.
- RT: effect in cognitive only.
- Heart rate: no effect.

@@

- Higher Yoni score associated with decreased lie confidence and increased truth confidence in polygraph condition only.
- Significant interactions.
- Driven by cognitive and physical domains.
- Polygraph condition is harder: participants with better TOM became less confident in absence of another person from which to obtain feedback cues?
- Plateau effect in interrogation condition, where individual differences do not matter as much?

@@

- Effect only in cognitive domain: higher score associated with slower lie reaction time in polygraph condition and faster truth reaction time in interrogation condition.
- No significant interaction.

@@

- Confidence: effect in all.
- RT: no effect.
- Heart rate: effect in all.

@@

- Higher BES score associated with decreased lie confidence and increased truth confidence in polygraph condition only.
- Same as Yoni.
- Significant interaction in lie only.
- Effect in lie driven by both cognitive and affective domains, effect in truth driven by affective domain only.

@@

- Higher BES score associated with increased lie and truth confidence in both conditions, with larger effect in interrogation condition.
- Compared to no effect at all in Yoni.
- Significant interactions.
- More empathetic person will experience more physiological arousals.
- Effect in interrogation is driven by both domains, effect in polygraph is driven by cognitive domain only.

### 2021-12-18 4_Intero.Rmd
minor edits
change social to interrogation
added interpretations

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

- Confidence: effect in all.
- RT: effect in confidence only.
- Heart rate: effect in accuracy and awareness.

@@

- Higher HCT accuracy score associated with increased lie confidence and decreased truth confidence in polygraph condition only.
- Significant interaction in truth only.

@@

- Higher HCT accuracy score associated with decreased lie heart rate in interrogation condition only.
- Significant interaction.
- Generally, larger effect in interrogation condition for heart rate?
- Plateau effect in polygraph condition for heart rate?

@@

- Higher HCT confidence score associated with increased lie confidence and decreased truth confidence in both conditions, with larger effect in polygraph condition.
- But no significant interaction.

@@

- Higher HCT confidence score associated with faster lie reaction time in polygraph condition and faster truth reaction time in both conditions.
- No significant interaction.

@@

- Higher HCT awareness score associated with decreased lie confidence in polygraph condition only.
- Significant interaction.

@@

- Higher HCT awareness score associated with decreased lie heart rate in interrogation condition only.
- Significant interaction.

@@

- Confidence: effect in total, noticing, not distracting, body listening, not worrying, attention regulation and self regulation.
- RT: effect in total, noticing, body listening, attention regulation and self regulation.
- Heart rate: effect in trusting and emotional awareness only.

@@

- Higher MAIA score associated with increased lie confidence in both conditions with a larger effect in polygraph condition, and decreased truth confidence in polygraph condition only.
- Significant interactions.
- Effect in lie driven by all domains except trusting and emotional awareness, effect in truth driven by noticing, attention regulation and self regulation domains.

@@

#### RT
- Higher MAIA score associated with faster truth reaction time in polygraph condition only.
- Significant interaction.
- Driven by body listening, attention regulation and self regulation domains.
- Faster lie reaction time in polygraph condition for noticing, body listening and attention regulation domains.

@@

- Effect only in trusting and emotional awareness domains: higher score associated with increased lie heart rate in interrogation for both, increased truth heart rate in interrogation for emotional awareness only.
- No significant interactions.
